\begin{thebibliography}{25}
	\bibitem {} D. E. Knuth, ``The TeXbook'', Addison--Wesley, 1984
	\bibitem {} Mc Leod, Raymond. ``Sistemas de Información Gerencial''. New Jersey, Prentice Hall, 1998
	\bibitem {} {\url{http://es.wikipedia.org/wiki/Sistemas_de_informaci%C3%B3n_gerencial}}
	\bibitem {} {\url{http://www.informatica-hoy.com.ar/aprender-informatica/Que-son-los-sistemas-de-gestion-empresarial.php}}
	\bibitem {} WeboPedia Computer Dictionary, ``What is a Support System?'', {\url{ http://www.webopedia.com/TERM/E/Executive_Support_System.html}} (Traducido), Disponible: 19 de Mayo del 2012
	\bibitem {} Alma López, ``Sistemas de Apoyo a Ejecutivos (Funciones no Comerciales)'',{\url{ http://es.scribd.com/doc/56124034/Sistemas-de-Apoyo-a-Ejecutivos}}, 2011, Disponible: 19 de Mayo del 2012.
	\bibitem {} Labor Omnia Vincent, ``Executive Support System (Funciones no Comerciales)'', {\url{http://es.scribd.com/doc/9657403/Executive-Support-Systems-ESS}}, 2009, Disponible 19 de Mayo del 2012.
	\bibitem {} {\url{http://meditech.com/MeditechEnEspanol/homepage.htm}}, Disponible: 19 de Mayo del 2012.
	\bibitem {} {\url{http://www.camsys.com/com_intro.htm}}, Disponible: 19 de Mayo del 2012.
	\bibitem {} {\url{http://es.wikipedia.org/wiki/Sistema_de_procesamiento_de_transacciones}}
	\bibitem {} {\url{http://en.wikipedia.org/wiki/Transaction_processing_system}}
	\bibitem {} {\url{http://es.wikipedia.org/wiki/ACID}}
	\bibitem {} {\url{http://www.transactionprocessingsystem.org}}
	\bibitem {} {\url{http://www.sinnexus.com/business_intelligence/sistemas_soporte_decisiones.aspx}} Disponible 21 de Mayo de 2012
	\bibitem {} {\url{http://es.wikipedia.org/wiki/Sistemas_de_soporte_a_decisiones}} Disponible 21 de Mayo de 2012
	\bibitem {} Keen, P. G. W. (1980). Decision support systems: a research perspective. Decision support systems : issues and challenges. G. Fick and R. H. Sprague. Oxford ; New York, Pergamon Press.
	\bibitem {} Haettenschwiler, P. (1999). Neues anwenderfreundliches Konzept der Entscheidungsunterstützung. Gutes Entscheiden in Wirtschaft, Politik und Gesellschaft. Zurich, vdf Hochschulverlag AG: 189-208.
	\bibitem {} Power, D. J. (2002). Decision support systems: concepts and resources for managers. Westport, Conn., Quorum Books.
	\bibitem {} Marakas, G. M. (1999). Decision support systems in the twenty-first century. Upper Saddle River, N.J., Prentice Hall.
	\bibitem {} {\url{http://dssmuisd.blogspot.com/2010/01/que-tipos-de-dss-existen.html}}, Disponible 21 de Mayo de 2012
	\bibitem {} {\url{http://es.scribd.com/doc/19726385/54/Desventajas-de-los-DSS}}, Disponible 21 de Mayo de 2012.
	\bibitem {} {\url{http://www.dssmexico.com/empresa/index.html}}, Disponible 21 de Mayo de 2012
	\bibitem {} {\url{http://www-935.ibm.com/services/us/gbs/bao/?cm_re=masthead-_-itservices-_-bao}}, Disponible 21 de Mayo de 2012
	\bibitem {} {\url{http://www.indigodss.com/}}
\end{thebibliography}
